Anti-Plagiarism System for Exam Monitoring

### 2025-06-24 Paper/Paper.tex
Made some tests for gaze tracking

\author{
    \IEEEauthorblockN{Valentin Pletea-Marinescu}
    \IEEEauthorblockA{
        \textit{National University of Science and Technology POLITEHNICA Bucharest}\\
        Email: \texttt{pletea.valentin2003@gmail.com}
    }
}

@@

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[
        scale=0.5,
        transform shape,
        node distance=1.0cm,
        start/.style={circle, fill=black, minimum width=0.5cm},
        end/.style={circle, draw=black, thick, fill=white, minimum width=0.5cm},
        process/.style={rectangle, draw=black, fill=blue!30, minimum width=2.8cm, 
                        minimum height=0.8cm, text centered, rounded corners},
        decision/.style={diamond, draw=black, fill=yellow!20, text centered, 
                        minimum width=1.8cm, minimum height=0.7cm, inner sep=0pt},
        arrow/.style={thick, ->, >=stealth}
    ]
        \node[start] (initpoint) {};
        \node[process, below of=initpoint] (start) {Start Monitoring};
        \node[process, below of=start, yshift=-0.1cm] (init) {Initialize Camera};

@@

\begin{equation}
\mathbf{F} = \begin{bmatrix}
1 & 0 & 1 & 0 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{bmatrix}
\end{equation}

Process noise covariance $\mathbf{Q} = 0.01 \times \mathbf{I}_4$ accounts for model uncertainties, while measurement noise adapts dynamically: $\mathbf{R} = \text{diag}(0.1/\text{confidence})$. The filter prediction step computes:

\begin{equation}
\mathbf{x}_{k|k-1} = \mathbf{F}\mathbf{x}_{k-1|k-1}
\end{equation}

\begin{equation}
\mathbf{P}_{k|k-1} = \mathbf{F}\mathbf{P}_{k-1|k-1}\mathbf{F}^T + \mathbf{Q}
\end{equation}

The correction step incorporates measurements with adaptive gain:

\begin{equation}
\mathbf{K}_k = \mathbf{P}_{k|k-1}\mathbf{H}^T(\mathbf{H}\mathbf{P}_{k|k-1}\mathbf{H}^T + \mathbf{R})^{-1}
\end{equation}

where $\mathbf{H} = [1, 0, 0, 0; 0, 1, 0, 0]$ extracts position measurements.

\subsubsection{Outlier Detection and Validation}

Euclidean distance outlier rejection ($d > 30$ pixels) prevents spurious measurements, while velocity constraints ($v_{max} = 50$ pixels/frame) ensure physically realistic tracking. Enhanced pupil detection incorporates contour circularity validation:

\begin{equation}
\text{Circularity} = \frac{4\pi \cdot \text{Area}}{\text{Perimeter}^2}
\end{equation}

with acceptance threshold $> 0.7$ and area constraints (0.01-0.3 × eye region) for robust performance under challenging conditions\cite{li2003survey}.

\subsubsection{Gaze Direction Classification}

The system computes horizontal and vertical gaze ratios using filtered pupil coordinates:

\begin{equation}
\text{Horizontal Ratio} = \frac{x_{pupil} - x_{eye\_left}}{x_{eye\_right} - x_{eye\_left}}
\end{equation}

\begin{equation}
\text{Vertical Ratio} = \frac{y_{pupil} - y_{eye\_top}}{y_{eye\_bottom} - y_{eye\_top}}
\end{equation}

Classification thresholds: left (HR $<$ 0.35), right (HR $>$ 0.65), down (VR $>$ 0.6), with center classification for intermediate values. Head pose compensation adjusts thresholds based on facial orientation angles derived from landmark geometry\cite{bar2001estimation}.

\subsection{Dual YOLOv8 Architecture Implementation}

The object detection framework employs specialized YOLOv8 models with unified 0.65 confidence threshold, optimized through systematic validation on dedicated training datasets. Implementation specifications:

\textbf{Model Architecture:} Dual-path detection pipeline processing smartphone (84\% accuracy, 4\% FPR) and smartwatch targets (81.6\% accuracy, 3\% FPR) with independent confidence thresholds and post-processing validation.

@@

The implementation successfully bridges the gap between advanced computer vision research and practical educational applications, providing institutions with accessible, cost-effective monitoring capabilities that maintain academic integrity standards while respecting privacy requirements and operational constraints.

>>>>

\author{
    \IEEEauthorblockN{Valentin Pletea-Marinescu}
    \IEEEauthorblockA{
        \textit{National University of Science and Technology POLITEHNICA Bucharest}\\
        Email: \texttt{valentin.pletea@stud.acs.upb.ro}
    }
    \IEEEauthorblockN{Ge Su}
    \IEEEauthorblockA{
        \textit{Zhejiang University}\\
        Email: \texttt{suge@zju.edu.cn}
    }
    \IEEEauthorblockN{Ștefan-Dan Ciocîrlan}
    \IEEEauthorblockA{
        \textit{National University of Science and Technology POLITEHNICA Bucharest}\\
        Email: \texttt{stefan\_dan.ciocirlan@upb.ro}
    }
    \IEEEauthorblockN{Ștefan-Alexandru Mocanu}
    \IEEEauthorblockA{
        \textit{National University of Science and Technology POLITEHNICA Bucharest}\\
        Email: \texttt{stefan.mocanu@upb.ro}
    }
}

@@

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[
        scale=0.45,
        transform shape,
        node distance=1.0cm,
        start/.style={circle, fill=black, minimum width=0.5cm},
        end/.style={circle, draw=black, thick, fill=white, minimum width=0.5cm},
        process/.style={rectangle, draw=black, fill=blue!30, minimum width=2.8cm, 
                        minimum height=0.8cm, text centered, rounded corners},
        decision/.style={diamond, draw=black, fill=yellow!20, text centered, 
                        minimum width=1.8cm, minimum height=0.7cm, inner sep=0pt},
        arrow/.style={thick, ->, >=stealth}
    ]
        \node[start] (initpoint) {};
        \node[process, below of=initpoint] (start) {Start Monitoring};
        \node[process, below of=start, yshift=-0.1cm] (init) {Initialize Camera};

@@

\begin{equation}
\mathbf{F} = \begin{bmatrix}
1 & 0 & 1 & 0 \\
0 & 1 & 0 & 1 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{bmatrix}
\end{equation}
Process noise covariance $\mathbf{Q} = 0.01 \times \mathbf{I}_4$ accounts for model uncertainties, while measurement noise adapts dynamically: $\mathbf{R} = \text{diag}(0.1/\text{confidence})$. The filter prediction step computes:
\begin{equation}
\mathbf{x}_{k|k-1} = \mathbf{F}\mathbf{x}_{k-1|k-1}
\end{equation}
\begin{equation}
\mathbf{P}_{k|k-1} = \mathbf{F}\mathbf{P}_{k-1|k-1}\mathbf{F}^T + \mathbf{Q}
\end{equation}
The correction step incorporates measurements with adaptive gain:
\begin{equation}
\mathbf{K}_k = \mathbf{P}_{k|k-1}\mathbf{H}^T(\mathbf{H}\mathbf{P}_{k|k-1}\mathbf{H}^T + \mathbf{R})^{-1}
\end{equation}
where $\mathbf{H} = [1, 0, 0, 0; 0, 1, 0, 0]$ extracts position measurements.
\subsubsection{Outlier Detection and Validation}
Euclidean distance outlier rejection ($d > 30$ pixels) prevents spurious measurements, while velocity constraints ($v_{max} = 50$ pixels/frame) ensure physically realistic tracking. Enhanced pupil detection incorporates contour circularity validation:
\begin{equation}
\text{Circularity} = \frac{4\pi \cdot \text{Area}}{\text{Perimeter}^2}
\end{equation}
with acceptance threshold $> 0.7$ and area constraints (0.01-0.3 × eye region) for robust performance under challenging conditions\cite{li2003survey}.
\subsubsection{Gaze Direction Classification}
The system computes horizontal and vertical gaze ratios using filtered pupil coordinates:
\begin{equation}
\text{Horizontal Ratio} = \frac{x_{pupil} - x_{eye\_left}}{x_{eye\_right} - x_{eye\_left}}
\end{equation}
\begin{equation}
\text{Vertical Ratio} = \frac{y_{pupil} - y_{eye\_top}}{y_{eye\_bottom} - y_{eye\_top}}
\end{equation}
Classification thresholds: left (HR $<$ 0.35), right (HR $>$ 0.65), down (VR $>$ 0.6), with center classification for intermediate values. Head pose compensation adjusts thresholds based on facial orientation angles derived from landmark geometry\cite{bar2001estimation}.
\subsection{Dual YOLOv8 Architecture Implementation}
The object detection framework employs specialized YOLOv8 models with unified 0.65 confidence threshold, optimized through systematic validation on dedicated training datasets. Implementation specifications:
\textbf{Model Architecture:} Dual-path detection pipeline processing smartphone (84\% accuracy, 4\% FPR) and smartwatch targets (81.6\% accuracy, 3\% FPR) with independent confidence thresholds and post-processing validation.

@@

The implementation successfully bridges the gap between advanced computer vision research and practical educational applications, providing institutions with accessible, cost-effective monitoring capabilities that maintain academic integrity standards.
